%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Presentaciones}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
%\vspace{-0.3cm}
%\begin{small}\textit{* presenting author; \textsuperscript{+} mentored undergraduate}\end{small}

%-------------------------------------------------------------------------------
%\cvsubsection{Invited Talks}
%-------------------------------------------------------------------------------

\begin{cvpubs}

    \cvpub {2025,\textbf{Vallone, A.} \& Olivares-Aremas, M,``Consumo de alcohol y accidentes de tránsito en Chile'',2025 RSA Annual Conference, University of Porto. Porto, Portugal}
    
    \cvpub {2025,Gonzalez, F \& \textbf{Vallone, A.} ,``Consumo de alcohol y accidentes de tránsito en Chile'',III Congreso RedCERT. Universidad Católica del Norte, Coquimbo, Chile}
     
     \cvpub {2024,\textbf{Vallone, A.} ,``Mapa de desigualdad de las caletas del área  costera de Chile'',II Congreso RedCERT , Universidad Católica de Temuco. Temuco, Chile}

    \cvpub {2023,\textbf{Vallone, A.} ,``Transformación Tecnológica del sector agrícola'',Seminario Internacional AGRO 5.0 , Universidad Católica de Cuyo. San Juan, Argentina}
    
    \cvpub{2002,Balaguera-Quintero, A., \textbf{Vallone, A.}, \& Igor-Tapia, S. (2022). Carbon footprint estimation for la serena-coquimbo conurbation based on global protocol for community-scale greenhouse gas emission inventories (gpc) ,7mo Encuentro de la Red de Centros de Estudios Regionales y Territoriales de Universidades Chilenas, Temuco, Chile}
    
    \cvpub{2022, \textbf{Vallone, A.} y Morales, C., ``Crisis hídrica en Chile, Acciones a nivel micro'', Segundo Conservatorio Regional sobre crisis h ́ıdrica, “¿Hay Agua en Argentina?”, Seminario online organizado por la Universidad Católica de Cuyo. San Juan, Argentina}
    
    \cvpub{2020, \textbf{Vallone, A.}, ``Beyond GDP: an analysis of the socio-economic diversity of European regions'', QuaRCS-lab Webinar Series 2020. Co-organized by the Japan Society for International Development (Tokai Branch) and Nagoya University’s Graduate School of International Development.}

    \cvpub{2018, \textbf{Vallone,A}. y Chasco, C., ``Spatio-temporal methods for the analysis of the Chilean urban system dynamics'', 17th Workshop on Spatial Econometrics and Statistics, Dijon, Francia}

    \cvpub{2017, \textbf{Vallone, A.} y Chasco, C., “Some strategies to access web-based urban spatial data for socioeconomic research using R.”, ECONRES Research Group Workshop, Madrid,España}

    \cvpub{2016, \textbf{Vallone, A.}, Chasco, C. y Atienza, M., ``Space, time and cities. Analysis of the concentration and dynamics of the Chilean urban system'', 63th North American Regional Science Council Meeting,, Minneapolis, E.E.U.U.}

    \cvpub{2016, \textbf{Vallone, A.}, Chasco, C. y Atienza, M., ``Space, time and cities. Analysis of the concentration and dynamics of the Chilean urban system'', AQR Research Group Seminar, Barcelona, España}

    \cvpub{2016, \textbf{Vallone, A.}, Chasco, C. y Atienza, M., ``Space, time and cities. Analysis of the concentration and dynamics of the Chilean urban system'', ECONRES Research Group Seminar, Madrid, España}

    \cvpub{2016, \textbf{Vallone, A.}, ``Discrete Markov Chain. Theory and use'', ECONRES Research Group Seminar, Madrid,España}

    \cvpub{2015,\textbf{Vallone, A. }y Atienza, M., ``Concentration, Development and the evolution of the urban system in Chile between 1885 and 2012'', 12th EU REAL Workshop, Madrid, España}    
\end{cvpubs}

%-------------------------------------------------------------------------------
